Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-09 manuscript/manuscript.Rmd
a bit of rewording

Reinforcement learning (RL) is a way of approaching *control problems* through machine learning.
An RL application can be conceptually separated into two parts: an *agent*, and an *environment*.
The *environment* is commonly a computer simulation, although it sometimes can be a real world system.
The *agent*, on the other hand, is a computer program which interacts with the environment.
That is, the agent may act on the environment and change its state.
This, moreover, gives the agent a *reward* which encodes the control goal.
The main part of an RL algorithm is then to progressively improve the agent's *policy*, in order to maximize the cumulative reward received. 
This is done by aggregating experience and learning from it.
See Fig. \ref{tbd}.

In our case, the environment will be a computational model of the population dynamics of a fishery, with the environment state being a vector of all the fish populations, $S=(V_1, V_2, H)$.
The system evolves naturally according to \eqref{eq:3d model}.
At each time step, the agent harvests one of the populations, say $A$. 
Specifically, it chooses a quota $q$: the fraction of $A$ that will be fished.
This changes the state as
\begin{align*}
  (V_1,\ V_2,\ H) \mapsto ((1-q)V_1,\ V_2,\ H)
\end{align*}
and secures a reward of $qV_1$ to the agent.
Afterwards, the environment undergoes its natural dynamics.

@@

As the name implies, the agent observes the full state of the environment of an FMDP, and chooses its next action based on this observation according to a *policy function* $\pi(a_t | s_t)$.
In return, the agent receives a discounted reward $\gamma^t r(a_t, s_t)$.
The discount factor helps regularize the agent, helping the optimization algorithm find solutions which pay off within a timescale of $t \sim \log(\gamma^{-1})$.

>>>>

Reinforcement learning (RL) is, in a nutshell, a way of approaching *control problems* through machine learning.
An RL algorithm can be conceptually separated into two parts: an *agent*, and an *environment* which the agent can interact with.
That is, the agent may act on the environment and thus change its state, while the environment gives a *reward* to the agent in return (see Fig. \ref{tbd}).
The rewards encode the agent's goal.
The main part of an RL algorithm is then to progressively improve the agent's *policy*, in order to maximize the cumulative reward received. 
This is done by aggregating experience and learning from it.

<!-- The *environment* is commonly a computer simulation, although it sometimes can be a real world system.
The *agent*, on the other hand, is a computer program which interacts with the environment. -->

For our use case, the environment will be a computational model of the population dynamics of a fishery, with the environment state being a vector of all the fish populations, $S=(V_1, V_2, H)$.
At each time step, the agent harvests one of the populations, $V_1$. 
This changes the state as
\begin{align*}
  (V_1,\ V_2,\ H) \mapsto ((1-q)V_1,\ V_2,\ H),
\end{align*}
where $q$ is a fishing *quota* set by the agent. 
This secures a reward of $qV_1$.
Afterwards, the environment undergoes a timestep under its natural dynamics given by \eqref{eq:3d model}.

@@

At a time $t$, the FMDP agent observes the full state $s_t$ of the environment and chooses an action based on this observation according to a *policy function* $\pi(a_t | s_t)$.
In return, it receives a discounted reward $\gamma^t r(a_t, s_t)$.
The discount factor helps regularize the agent, helping the optimization algorithm find solutions which pay off within a timescale of $t \sim \log(\gamma^{-1})^{-1}$.
